---
title: "jeksterslabRdata"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jeksterslabds/jeksterslabRdata.svg?branch=master)](https://travis-ci.com/jeksterslabds/jeksterslabRdata)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jeksterslabds/jeksterslabRdata?branch=master&svg=true)](https://ci.appveyor.com/project/jeksterslabds/jeksterslabRdata)
[![codecov](https://codecov.io/github/jeksterslabds/jeksterslabRdata/branch/master/graphs/badge.svg)](https://codecov.io/github/jeksterslabds/jeksterslabRdata) 
<!-- badges: end -->

`jeksterslabRdata` is a collection of functions that I find useful in studying data generation and sampling.

## Installation

You can install the released version of `jeksterslabRdata` from [GitHub](https://github.com/jeksterslabds/jeksterslabRdata) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRdata")
```

## Documentation

See [GitHub Pages](https://jeksterslabds.github.io/jeksterslabRdata/index.html)
for package documentation.

## Main functions

```{r}
library(jeksterslabRdata)
```

### `univ()`

Generates an `n x 1` univariate data vector
or a list of `n x 1` univariate data vectors of length `R`.
The default data generating function
is the normal distribution.

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225))
```

Explore the output.

```{r}
str(x, list.len = 6)
hist(x, main = expression(italic(N)(list(mu == 100, sigma^2 == 225))))
```

#### Multiple Random Data Sets

Run the function.

```{r}
xstar <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225), R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```

### `mvn()`

Generates an `n x k` multivariate data matrix
or a list of `n x k` multivariate data matrices of length `R`
from the multivariate normal distribution.
This function is a wrapper around `MASS::mvrnorm()`.

#### Single Random Data Set

Set `mu` and `Sigma`.

```{r}
mu <- c(100, 100, 100)
Sigma <- matrix(
  data = c(225, 112.50, 56.25, 112.5, 225, 112.5, 56.25, 112.50, 225),
  ncol = 3
)
```

Run the function.

```{r}
X <- mvn(n = 100, mu = mu, Sigma = Sigma)
```

Explore the output.

```{r}
str(X)
pairs(X)
colMeans(X)
cov(X)
cor(X)
```

#### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvn(n = 100, mu = mu, Sigma = Sigma, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```

### `mvnram()`

Generates an `n x k` multivariate data matrix
or a list of `n x k` multivariate data matrices of length `R`
from the multivariate normal distribution.
The model-implied matrices used to generate data
is derived from the Reticular Action Model (RAM) Matrices.

#### Single Random Data Set

Set matrices.

```{r}
mu <- c(100, 100, 100)
A <- matrix(
  data = c(0, sqrt(0.26), 0, 0, 0, sqrt(0.26), 0, 0, 0),
  ncol = 3
)
S <- diag(c(225, 166.5, 116.5))
F <- I <- diag(3)
```

Run the function.

```{r}
X <- mvnram(n = 100, mu = mu, A = A, S = S, F = F, I = I)
```

Explore the output.

```{r}
str(X)
pairs(X)
colMeans(X)
cov(X)
cor(X)
```

#### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvnram(n = 100, mu = mu, A = A, S = S, F = F, I = I, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```
