---
title: "Introduction to jeksterslabRdata"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Learn how to get started with the basics of jeksterslabRdata.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to jeksterslabRdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`jeksterslabRdata` is a collection of functions that I find useful in studying data generation and sampling.

## Installation

You can install the released version of `jeksterslabRdata` from [GitHub](https://github.com/jeksterslabds/jeksterslabRdata) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRdata")
```

## Main functions

```{r}
library(jeksterslabRdata)
```

### `univ()`

Generates an $n \times 1$ univariate data vector
or a list of $n \times 1$ univariate data vectors of length `R`.
The default data generating function
is the normal distribution

\begin{equation}
  X \sim \mathcal{N} \left( \mu, \sigma^2 \right) .
  %(\#eq:dist-X-norm)
\end{equation}

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225))
```

Explore the output.

```{r}
str(x, list.len = 6)
hist(x, main = expression(italic(N)(list(mu == 100, sigma^2 == 225))))
```

#### Multiple Random Data Sets

Run the function.

```{r}
xstar <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225), R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```

### `mvn()`

Generates an $n \times k$ multivariate data matrix
or a list of $n \times k$ multivariate data matrices of length `R`
from the multivariate normal distribution

\begin{equation}
  \mathbf{X} \sim \mathcal{N}_{k}
  \left( \boldsymbol{\mu}, \boldsymbol{\Sigma} \right) .
  %(\#eq:dist-X-mvn)
\end{equation}

\noindent This function is a wrapper around `MASS::mvrnorm()`.

#### Single Random Data Set

Set `mu` and `Sigma`.

```{r}
mu <- c(100, 100, 100)
Sigma <- matrix(
  data = c(225, 112.50, 56.25, 112.5, 225, 112.5, 56.25, 112.50, 225),
  ncol = 3
)
```

Run the function.

```{r}
X <- mvn(n = 100, mu = mu, Sigma = Sigma)
```

Explore the output.

```{r}
str(X)
psych::pairs.panels(X)
colMeans(X)
cov(X)
cor(X)
```

#### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvn(n = 100, mu = mu, Sigma = Sigma, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```

### `mvnram()`

Generates an $n \times k$ multivariate data matrix
or a list of $n \times k$ multivariate data matrices of length `R`
from the multivariate normal distribution

\begin{equation}
  \mathbf{X} \sim \mathcal{N}_{k}
  \left( \boldsymbol{\mu}, \boldsymbol{\Sigma} \right) .
  %(\#eq:dist-X-mvn)
\end{equation}

\noindent The model-implied matrices used to generate data
is derived from the Reticular Action Model (RAM) Matrices.

#### Single Random Data Set

Set matrices.

```{r}
mu <- c(100, 100, 100)
A <- matrix(
  data = c(0, sqrt(0.26), 0, 0, 0, sqrt(0.26), 0, 0, 0),
  ncol = 3
)
S <- diag(c(225, 166.5, 116.5))
F <- I <- diag(3)
```

Run the function.

```{r}
X <- mvnram(n = 100, mu = mu, A = A, S = S, F = F, I = I)
```

Explore the output.

```{r}
str(X)
psych::pairs.panels(X)
colMeans(X)
cov(X)
cor(X)
```

#### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvnram(n = 100, mu = mu, A = A, S = S, F = F, I = I, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```
