---
title: "Examples for the fit() function"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Examples for the fit() function.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Examples for the fit() function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(jeksterslabRdata)
```

## Documentation

See `fit()` for more details.

## Examples

### `univ()`

#### Normal Distribution

##### Generate Data

```{r}
xstar <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225), R = 100)
```

##### Fit the `mean()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = mean, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(mu)),
  xlab = expression(hat(mu))
)
```

##### Fit the `var()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = var, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(sigma)^2),
  xlab = expression(hat(sigma)^2)
)
```

#### Bernoulli Distribution

##### Generate Data

```{r}
xstar <- univ(n = 100, rFUN = rbinom, size = 1, prob = 0.50, R = 100)
```

##### Fit the `mean()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = mean, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(mu)),
  xlab = expression(hat(mu))
)
```

##### Fit the `var()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = var, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(sigma)^2),
  xlab = expression(hat(sigma)^2)
)
```

#### Binomial Distribution

##### Generate Data

```{r}
xstar <- univ(n = 100, rFUN = rbinom, size = 40, prob = 0.50, R = 100)
```

##### Fit the `mean()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = mean, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(mu)),
  xlab = expression(hat(mu))
)
```

##### Fit the `var()` Function Using `fit()`

Run the function.

```{r}
thetahatstar <- fit(Xstar = xstar, fitFUN = var, rbind = TRUE)
```

Explore the output.

```{r}
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(sigma)^2),
  xlab = expression(hat(sigma)^2)
)
```

### `mvn()`

##### Generate Data

```{r}
Sigma <- matrix(
  data = c(1, 0.50, 0.50, 1),
  ncol = 2
)
Xstar <- mvn(n = 100, Sigma = Sigma, R = 100)
```

##### Fit a custom `cov()` Function Using `fit()`

Run the function.

```{r}
foo <- function(X) {
  as.vector(cov(X))
}
thetahatstar <- fit(Xstar = Xstar, fitFUN = foo, rbind = TRUE)
```

Explore the output.

```{r}
thetahatstar <- thetahatstar[, 2]
str(thetahatstar)
hist(thetahatstar,
  main = expression("Sampling distribution of" ~ hat(rho)),
  xlab = expression(hat(rho))
)
```
