---
title: "Examples for the univ() function"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Examples for the univ() function.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Examples for the univ() function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(jeksterslabRdata)
```

## Documentation

See `univ()` for more details.

## Examples

### Normal Distribution

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225))
```

Explore the output.

```{r}
str(x, list.len = 6)
hist(x, main = expression(italic(N)(list(mu == 100, sigma^2 == 225))))
```

#### Multiple Random Data Sets

Run the function.

```{r}
xstar <- univ(n = 100, rFUN = rnorm, mean = 100, sd = sqrt(225), R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```

### Bernoulli Distribution

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rbinom, size = 1, prob = 0.50)
```

Explore the output.

```{r}
str(x, list.len = 6)
barplot(table(x), main = expression(italic("Bernoulli")(p == 0.50)))
```

#### Multiple Random Data Sets

Run the function.

```{r}
x <- univ(n = 100, rFUN = rbinom, size = 1, prob = 0.50, R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```

### Binomial Distribution

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rbinom, size = 20, prob = 0.50)
```

Explore the output.

```{r}
str(x, list.len = 6)
barplot(table(x), main = expression(italic("Binomial")(list(n == 20, p == 0.50))))
```

#### Multiple Random Data Sets

Run the function.

```{r}
x <- univ(n = 100, rFUN = rbinom, size = 20, prob = 0.50, R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```

### Exponential Distribution

#### Single Random Data Set

Run the function.

```{r}
x <- univ(n = 100, rFUN = rexp, rate = 1)
```

Explore the output.

```{r}
str(x, list.len = 6)
hist(x, main = expression(italic(exp)(lambda == 1)))
```

#### Multiple Random Data Sets

Run the function.

```{r}
xstar <- univ(n = 100, rFUN = rexp, rate = 1, R = 100)
```

Explore the output.

```{r}
str(xstar, list.len = 6)
```
