---
title: "Examples for the mvnramsigma2() function"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Examples for the mvnramsigma2() function.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Examples for the mvnramsigma2() function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(jeksterslabRdata)
```

## Documentation

See `mvnramsigma2()` for more details.

## Examples

### Specify `mu`

#### Single Random Data Set

Set matrices.

```{r}
mu <- c(100, 100, 100)
A <- matrix(
  data = c(0, sqrt(0.26), 0, 0, 0, sqrt(0.26), 0, 0, 0),
  ncol = 3
)
sigma2 <- c(225, 225, 225)
F <- I <- diag(3)
```

Run the function.

```{r}
X <- mvnramsigma2(n = 100, mu = mu, A = A, sigma2 = sigma2, F = F, I = I)
```

Explore the output.

```{r}
str(X)
psych::pairs.panels(X)
colMeans(X)
cov(X)
cor(X)
```

### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvnramsigma2(n = 100, mu = mu, A = A, sigma2 = sigma2, F = F, I = I, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```

### Specify `M`

#### Single Random Data Set

Set matrices.

```{r}
M <- c(100, 50, 50)
A <- matrix(
  data = c(0, sqrt(0.26), 0, 0, 0, sqrt(0.26), 0, 0, 0),
  ncol = 3
)
sigma2 <- c(225, 225, 225)
F <- I <- diag(3)
```

Run the function.

```{r}
X <- mvnramsigma2(n = 100, M = M, A = A, sigma2 = sigma2, F = F, I = I)
```

Explore the output.

```{r}
str(X)
psych::pairs.panels(X)
colMeans(X)
cov(X)
cor(X)
```

### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvnramsigma2(n = 100, M = M, A = A, sigma2 = sigma2, F = F, I = I, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```

### Specify `mu = NULL` and `M = NULL`

#### Single Random Data Set

Set matrices.

```{r}
A <- matrix(
  data = c(0, sqrt(0.26), 0, 0, 0, sqrt(0.26), 0, 0, 0),
  ncol = 3
)
sigma2 <- c(225, 225, 225)
F <- I <- diag(3)
```

Run the function.

```{r}
X <- mvnramsigma2(n = 100, A = A, sigma2 = sigma2, F = F, I = I)
```

Explore the output.

```{r}
str(X)
psych::pairs.panels(X)
colMeans(X)
cov(X)
cor(X)
```

### Multiple Random Data Sets

Run the function.

```{r}
Xstar <- mvnramsigma2(n = 100, A = A, sigma2 = sigma2, F = F, I = I, R = 100)
```

Explore the output.

```{r}
str(Xstar, list.len = 6)
```
